Development of a permanent magnet characterisation framework for use in low-field MRI systems

### 2024-02-27 documentation/colloquium/presentation/index.qmd
.

<p class="fragment">&#x2022; Permanent magnets differ in their field strength due to their manufacture process and environmental changes</p>

<p class="fragment">&#x2022; This influences the homogeneity of the assembled magnet</p>

<p class="fragment">&#x2022; This influences the homogeneity of the assembled magnet</p>
<p class="fragment">&#x2022; It can be improved by means of a complex shimming process</p>

@@

<p class="fragment"> Measure magnets in advance</p>
<p class="fragment"> Execute optimization or sorting algorithms on the magnet field data</p>
<p class="fragment"> Buld an optimized magnet</p>

@@

<p class="fragment">Projects exists that follow this approach but only implement individual parts</p>
<p class="fragment">Incompatible dataformats</p>
<p class="fragment">Complex magnetic field sensor integrations</p>
<p class="fragment">Usage of non opensource software</p>
<aside class="notes">
* diverse projekte welche einzelne algrothmen dazu haben
* jedoch nicht kompatible zueinander

@@

<p class="fragment">Provides and user-oriented **open** magnetic field data hardware and software framework:</p>
<br />
<p class="fragment">&#x2022; Harware support for several magnetic field sensors</p>
<br />
<p class="fragment">&#x2022; Ready to use data analysis pipelines</p>
<br />
<p class="fragment">&#x2022; Easy to integrate and extend into existing projects</p>

@@

Cheap and easy to construct sensors using consumer grade magnetic field sensors:
<br />
<br />
<p class="fragment">&#x2022; One software for most common digital magnetic field sensors</p>
<br />
<p class="fragment">&#x2022; Synchronised multi sensor setups</p>
<br />
<p class="fragment">&#x2022; Universal and interachangable magnet mount</p>

@@

Allows rapid development of software analysation functions, without implementation of typical data processing pipelines providing:

@@

<aside class="notes">
* messdaten und meta-daten management
* integration zu andern projekten magpylib, matlab, 
* analysepipeline schauen wir uns später an
* volle doku, getestet

>>>>

<p class="fragment">&#x2022; Permanent magnets differ in their field strength due to their manufacturing process and environmental changes</p>
<p class="fragment">&#x2022; This influences the homogeneity of the assembled magnet</p>
<p class="fragment">&#x2022; It can be improved by means of a complex shimming process</p>

@@

<p class="fragment">&#x2022; Measure magnets in advance</p>
<p class="fragment">&#x2022; Execute optimization or sorting algorithms on the magnet field data</p>
<p class="fragment">&#x2022; Build an optimized magnet</p>

<aside class="notes">
* diverse projekte welche einzelne algrothmen dazu haben
* jedoch nicht kompatible zueinander

<p class="">&#x2022; Measure magnets in advance</p>
<p class="">&#x2022; Execute optimization or sorting algorithms on the magnet field data</p>
<p class="">&#x2022; Build an optimized magnet</p>

@@

<p class="fragment">&#x2022; Existing projects follow this approach but only implement individual parts</p>
<p class="fragment">&#x2022; Incompatible data-formats</p>
<p class="fragment">&#x2022; Complex magnetic field sensor integrations</p>
<p class="fragment">&#x2022; Usage of non open source software</p>
<aside class="notes">
* diverse projekte welche einzelne algrothmen dazu haben
* jedoch nicht kompatible zueinander

@@

<p class="fragment">Provides and user-oriented **open** magnetic field hardware and software framework:</p>
<br />
<p class="fragment">&#x2022; Hardware support for several magnetic field sensors</p>
<br />
<p class="fragment">&#x2022; Ready to use data analysis pipelines</p>
<br />
<p class="fragment">&#x2022; Easy to integrate and extend into existing projects</p>

@@

Cheap and easy to construct magnetic field sensors:
<br />
<br />
<p class="fragment">&#x2022; One software for most common digital magnetic field sensors</p>
<br />
<p class="fragment">&#x2022; Synchronised multi sensor setups</p>
<br />
<p class="fragment">&#x2022; Universal and interchangeable mount for different magnet shapes</p>

@@

Provides rapid development of analysis functions without the need to implement typical data processing pipelines:

@@

<aside class="notes">
* mit der hardware können wird magnetfeld daten aufnehmen
* jetzt fehlt noch die software dazu
* messdaten und meta-daten management
* integration zu andern projekten magpylib, matlab, 
* analysepipeline schauen wir uns später an
* volle doku, getestet
